Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex

### 2019-03-29 Manuscript.Rmd
small tweaks

``` {r For HCP data, fig.align="center", echo=FALSE, message = FALSE}
setwd('./For_HCP')
temp <- list.files(pattern = '*Binary*')
FB <- lapply(temp, read.table)
Summed <- do.call(cbind, lapply(FB, "[[", 'V1')) - 1
FB_Means <- rowMeans(Summed)
nSubj <- length(temp)
rm(temp)
```

@@

  In this study, we aimed to subdivide regions commonly attributed to both DMN and subjective valuation into individual-specific DMN and non-DMN communities, quantifying the degree of topographical heterogeneity present in this network within and across individuals. We did this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain networks. First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DMN and limbic networks along the medial cortical wall [@Yeo2011]. A cortical surface-based meta-analysis of DMN and SV literatures identified a parcel in PCC that was DMN-specific at the aggregate level. We then derived an rsFC network of all the surface vertices within the search space for each of 100 individual resting-state fMRI data sets from the Human Connectome Project (HCP)[@VanEssen2012], and used the SP algorithm to subdivide each individual's network into DMN and non-DMN communities (defined according to the degree of coverage of the PCC parcel). Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographical extent of each community. The resulting communities varied topographically across subjects, while also appearing to follow common organizational principles. A combination of sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that this idiosyncrasy was higher in mPFC. Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity. Lastly, we provide evidence that the resulting communities resembled an organizational scheme recently observed in a handful of subjects [@Braga2017]. Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.

>>>>

``` {r For HCP data, fig.align="center", echo=FALSE, message = FALSE}
# this is used to get the number of subjects and proportion maps for the group (for visualization only)
setwd('./For_HCP')
temp <- list.files(pattern = '*Binary*')
FB <- lapply(temp, read.table)
Summed <- do.call(cbind, lapply(FB, "[[", 'V1')) - 1
FB_Means <- rowMeans(Summed)
nSubj <- length(temp)
rm(temp)
```

@@

  In this study, we aimed to subdivide regions commonly attributed to both DMN and subjective valuation into individual-specific DMN and non-DMN communities, quantifying the degree of topographical heterogeneity present in this network within and across individuals. We did this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain networks. First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DMN and limbic networks along the medial cortical wall [@Yeo2011]. A cortical surface-based meta-analysis of DMN and SV literatures identified a parcel in PCC that was DMN-specific at the aggregate level. We then derived an rsFC network of all the surface vertices within the search space for each of `r nSubj` individual resting-state fMRI data sets from the Human Connectome Project (HCP)[@VanEssen2012], and used the SP algorithm to subdivide each individual's network into DMN and non-DMN communities (defined according to the degree of coverage of the PCC parcel). Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographical extent of each community. The resulting communities varied topographically across subjects, while also appearing to follow common organizational principles. A combination of sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that this idiosyncrasy was higher in mPFC. Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity. Lastly, we provide evidence that the resulting communities resembled an organizational scheme recently observed in a handful of subjects [@Braga2017]. Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.
